---
title: "Exp - HardAndSparse review"
output: html_notebook
---

# Libraries
```{r, message=FALSE}
library(zoo)
library(ggplot2)
library(ggpubr)
library(patchwork)
library(tidyr)
library(dplyr)
library(gridExtra)
library(grid)
library(readr)
library(latex2exp)
# library(MASS) 
library(scales)
library(patchwork)
options(scipen=1000000)

# Load load_result and other helpful functions
source("utils.R")

# --- Main path to all data ---
data_path <- "~/Code/infomercial/data/"
```

# The problem
- Most simulation have showed a clear advantage for meta with the BanditHardAndSparse10 task
- But! Some later runs, with what should be better HP search, don't show this.
- Meta is instead middle of the pack. Which is unexpected.
- In this notebook I explore a range of past simulations and HPs to try and understand.

# Data bibliography
Meta
- exp535 (exp387_sorted, initial_bins) **
- exp429 (exp387_sorted, num_episodes=40000) **
- exp546 (exp387_sorted, num_episodes=60000) **
- exp428 (exp427_sorted, tie_threshold='(1e-11, 1e-2))
- exp408 (exp387_sorted, num_episodes=20000)

Other
- exp431: anneal-ep (exp386_sorted)
- exp433: random example

# Load data
```{r, message=FALSE}
# -------------------------------------------------------------
task_name <- "BanditHardAndSparse10"
task_code <- 2

exp_names <- c(
  "exp535", 
  "exp546", 
  "exp429", 
  "exp428", 
  "exp408", 
  "exp431", 
  "exp433")

num_episodes <- c(50000, 
                  60000, 
                  40000, 
                  20000, 
                  20000, 
                  40000, 
                  40000)

agent_names <- c(
  "Curiosity535", 
  "Curiosity546", 
  "Curiosity429", 
  "Curiosity428", 
  "Curiosity408",
  "tau-random431", 
  "Random")

file_names <- c("score_R", 
                "action", 
                "p_bests", 
                "regret", 
                "total_R",
                "total_E",
                "total_regret")

result_task2<- NULL
summary_task2 <- NULL
summary_task2_short <- NULL
for(i in 1:length(exp_names)){
  exp_name <- exp_names[i]
  agent_name <- agent_names[i]
  num_episode <- num_episodes[i] / 1
  
  if (agent_name == "Random"){
    param_codes <- c(0)
    run_codes <- 1:10
  } else{
    param_codes <- 0:9
    run_codes <- 1:10
  }
  
  tmp1 <- load_result(exp_name, param_codes, run_codes, file_names, 
                      n_max = num_episode)
  
  tmp1$exp <- exp_name
  tmp1$agent <- agent_name
  tmp1$task <- task_name
  tmp1$task_code <- task_code
  tmp1$num_episodes <- num_episode
  result_task2 <- bind_rows(result_task2, tmp1)
  
}

# Final episodes results (all params/runs)
result_task2 %>% 
  group_by(agent, param, run) %>% 
  summarise(total_R = last(total_R),
            total_E = last(total_E),
            total_value = last(total_R) + last(total_E),
            total_regret = last(total_regret),
            p_bests = last(p_bests)) %>% 
  ungroup() -> final_task2

# Summary stats for final values
final_task2 %>% 
  group_by(agent) %>% 
  summarise(median_R = median(total_R), 
            var_R = mad(total_R),
            median_E = median(total_E), 
            var_E = mad(total_E),
            median_total_value = median(total_value), 
            var_total_value = mad(total_value),
            median_regret = median(total_regret),
            var_regret = mad(total_regret),
            median_p_bests=median(p_bests),
            var_p_bests=mad(p_bests)) %>% 
  ungroup() -> 
  summary_task2

rm(tmp1, agent_name, agent_names, exp_name, exp_names, file_names, 
   i, param_codes, run_codes, task_name)
```

# Fig. actions
```{r, fig.width=3, fig.height=1.4}
p <- 10
r <- 3

num_arm <- max(result_task2$action) + 1

result_task2 %>% 
  filter(param <= p, run == r) %>% 
  ggplot(aes(x=global_step, y=action+1)) +
  geom_point(size=0.2, alpha=0.9, color="black") +
  geom_line(size=0.1) +
  scale_x_continuous(
    limits=c(0, num_episode+(num_episode*.1)), 
    breaks = c(0, num_episode)) +
  scale_y_continuous(limits=c(0, num_arm+1), breaks = 1:num_arm) +
  labs(x="Time", y="Action") +
  facet_grid(agent~param) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(.1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(plot.title = element_text(size = 6)) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) 
```
# Fig. Reward (time)
```{r, fig.width=3.2, fig.height=0.7}
p <- 2
r <- 10

result_task2 %>% 
  filter(global_step > 10) %>% 
  filter(param <= p, run <= r) %>% 
  ggplot(aes(x=global_step, y=total_R/global_step, 
             group=interaction(param,run))) +
  geom_line(size=0.1, alpha=1, shape=".") +
  scale_x_continuous(limits=c(0, num_episodes),
                     breaks = c(0, num_episodes)) +
  scale_y_continuous(limits=c(0, 0.022),
                     breaks = c(0, 0.01, 0.02)) +
  facet_wrap(agent~., nrow=1) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(panel.spacing = unit(1, "lines")) +
  theme(strip.background = element_blank()) 
```

# Fig. summary
```{r, fig.width=2.4, fig.height=0.8}
final_task2 %>% 
  ggplot(aes(x=agent, y=total_R/num_episode)) +
  geom_jitter(width=0.1, alpha=0.6, shape=".") +
  stat_summary(fun=median, alpha=1, color="black", size=0.6, shape="|") +
  scale_y_continuous(limits=c(-.001, 0.03), breaks = c(0, 0.01, 0.02)) +
  labs(x="", y="Average reward") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  coord_flip() -> p1

final_task2 %>% 
  ggplot(aes(x=agent, y=total_value/num_episode)) +
  geom_jitter(width=0.1, alpha=0.6, shape=".") +
  stat_summary(fun=median, alpha=1, color="black", size=0.6, shape="|") +
  scale_y_continuous(limits=c(-.001, 0.03), breaks = c(0, 0.015, 0.03)) +
  labs(x="", y="Average value") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(axis.text.y = element_blank()) +
  theme(strip.background = element_blank()) +
  coord_flip() -> p2

final_task2 %>% 
  ggplot(aes(x=agent, y=total_regret/num_episode)) +
  geom_jitter(width=0.1, alpha=0.6, shape=".") +
  stat_summary(fun=median, alpha=1, color="black", size=0.5, shape="|") +
  labs(x="", y="Average regret") +
  scale_y_continuous(limits=c(-.001, 0.06), breaks = c(0, 0.025, 0.05)) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(axis.text.y = element_blank()) +
  coord_flip() -> p3

final_task2 %>% 
  ggplot(aes(x=agent, y=p_bests)) +
  geom_jitter(width=0.1, alpha=0.6, shape=".") +
  stat_summary(fun=median, alpha=1, color="black", size=0.6, shape="|") +
  scale_y_continuous(limits=c(-.1, 1.1), breaks = c(0, 0.5, 1)) +
  labs(x="", y="P(best)") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(axis.text.y = element_blank()) +
  coord_flip() -> p4

p1 + p2 + p3 + p4 + plot_layout(nrow=1)
```

