---
title: "Figures"
output: html_notebook
---

# Imports and paths
```{r, message=FALSE}
library(zoo)
library(ggplot2)
library(ggpubr)
library(patchwork)
library(tidyr)
library(dplyr)
library(gridExtra)
library(grid)
library(readr)
library(latex2exp)
library(MASS) 
library(scales)
library(patchwork)
options(scipen=1000000)

kl_divergence <- function(p, q) {
  sum(p * log(p/q))
}

# --- Main path to all data ---
data_path <- "~/Code/infomercial/data/"
```

# Figure - Curiosity in a random world
## Load data
```{r message=FALSE, cache=TRUE}
# ---
exp_name <- "exp348"

actor_names <- c("DeterministicActor", "SoftmaxActor", "RandomActor")
better_names <- c("Deterministic", "Stochastic", "Random")

run_codes <- 1:100
file_names <- c("score_E", "action", "p_bests", "regret", "value_E", 
                "ties", "state", "total_E", "total_regret")

# ---
result348 <- NULL
for (i in 1:length(actor_names)){
  actor <- actor_names[i]
  better <- better_names[i]
  for (run in run_codes) {
    runtmp <- read_csv(paste(data_path, 
                             exp_name, 
                             actor,
                             paste("run", run, sep=""), 
                             paste(file_names[1], "csv", sep="."), sep="/"))    
    for (name in file_names[2:9]){
      tmp <- read_csv(paste(data_path, 
                            exp_name, 
                            actor,
                            paste("run", run, sep=""), 
                            paste(name, "csv", sep="."), sep="/"))  
      runtmp[[name]] <- tmp[[name]]
    }
    runtmp$run <- run
    runtmp$actor <- better
    runtmp$num_trials <- nrow(tmp)
    result348 <- bind_rows(result348, runtmp)  
  }
}

# --- Summarize the results ---
Ebias <- 4*1.38

result348 %>% 
  group_by(actor, run) %>% 
  summarise(
    total_E=max(total_E),
    total_regret=max(total_regret),
    value_E=mean(value_E),
    regret=mean(regret[regret > 0]),
    num_steps=max(num_trials)
  ) %>% 
  ungroup() ->
summary348

# --
summary348$actor <- factor(summary348$actor, 
                           levels=c("Deterministic", "Stochastic", "Random"))

# ---
rm(tmp, runtmp, run, name, better, i)
```

## Sub 1 - examples
```{r, fig.width=1.6, fig.height=2.2}
result348 %>% 
  filter(actor == "Deterministic") %>% 
  # filter(global_step < 40) %>%
  filter(run <= 12) %>% 
  ggplot(aes(x=global_step, y=action, color=actor)) +
  lims(x=c(0, 320)) +
  geom_line(size=0.3, alpha=1) +
  labs(x="", y="Choice", title="Deterministic") +
  facet_wrap(.~run, ncol=1) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  scale_color_manual("Search", values=c("mediumorchid4")) +
  theme(panel.spacing = unit(0.1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(plot.title = element_text(size = 6)) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.text.x = element_blank()) +
  # theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks = element_blank()) + 
  theme(legend.key.size = unit(0.2, "cm")) -> 
  p1

result348 %>% 
  filter(actor == "Stochastic") %>% 
  filter(run <= 12) %>% 
  ggplot(aes(x=global_step, y=action, color=actor)) +
  lims(x=c(0, 320)) +
  geom_line(size=0.3, alpha=1) +
  labs(x="", y="", title="Stochastic") +
  facet_wrap(.~run, ncol=1) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  scale_color_manual("Search", values=c("dodgerblue4")) +
  theme(panel.spacing = unit(0.1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(plot.title = element_text(size = 6)) +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.text.x = element_blank()) +
  # theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks = element_blank()) + 
  theme(legend.key.size = unit(0.2, "cm")) -> 
  p2

# ---
result348 %>% 
  filter(run == 42) %>% 
  filter(global_step > 5) %>%
  filter(actor != "Random") %>% 
  ggplot(aes(x=global_step, y=value_E, color=actor)) +
  geom_vline(aes(xintercept=min(num_trials)), 
             color="black", linetype="dashed", alpha=0.9, size=0.2) +
  geom_line(size=0.8, alpha=1) +
  lims(x=c(0, 320)) +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  facet_wrap(.~actor) +
  labs(x="", y="Value") + 
  scale_color_manual("", values=c("darkorchid4", "dodgerblue4")) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(panel.spacing = unit(1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(strip.text.x = element_blank()) -> p3

result348 %>% 
  filter(run == 42) %>% 
  filter(global_step > 5) %>%
  filter(actor != "Random") %>% 
  ggplot(aes(x=global_step, y=regret, color=actor)) +
  geom_line(size=0.8, alpha=1) +
  lims(x=c(0, 320)) +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  facet_wrap(.~actor) +
  labs(x="Time", y="Regret") + 
  scale_color_manual("", values=c("darkorchid4", "dodgerblue4")) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) +
  theme(strip.text.x = element_blank()) -> p4


c1 <- (p1 + p2) / p3 / p4 + 
  plot_layout(heights = c(0.7, 0.15, 0.15)) 
```

## Sub 2 - dists (jitter)
```{r, fig.height=2, fig.width=0.8}
# average value
summary348 %>% 
  ggplot(aes(x=actor, y=value_E, color=actor)) +
  geom_jitter(size=0.3, alpha=0.9, width=0.2) +
  stat_summary(fun=mean, color="black", alpha=0.9, size=2, shape="-") +
  scale_colour_manual("", values=c("mediumorchid4", "dodgerblue4", "darkgray")) +
  labs(x="", y="Average value") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) +
  theme(axis.text.x = element_blank()) -> 
  p1

# steps
summary348 %>% 
  ggplot(aes(x=actor, y=num_steps, color=actor)) +
  geom_jitter(size=0.3, alpha=0.9, width=0.2) +
  stat_summary(fun=mean, color="black", alpha=0.9, size=2, shape="-") +
  scale_colour_manual("", values=c("mediumorchid4", "dodgerblue4", "darkgray")) +
  labs(x="", y="Steps") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) +
  theme(axis.text.x = element_blank()) -> 
  p2

# average regret
summary348 %>% 
  ggplot(aes(x=actor, y=total_regret, color=actor)) +
  geom_jitter(size=0.3, alpha=0.9, width=0.2) +
  stat_summary(fun=mean, color="black", alpha=0.9, size=2, shape="-") +
  scale_colour_manual("", values=c("mediumorchid4", "dodgerblue4", "darkgray")) +
  labs(x="", y="Total regret") +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(panel.spacing = unit(1, "lines")) ->
  p3

# ---
c2 <- p1 / p2 / p3 
```

## Build figure
```{r, fig.height=2.6, fig.width=2}
fig <- (c1 | c2 + plot_spacer()) + 
  plot_layout(widths = c(0.75, 0.25)) +
    plot_annotation(
      title="Deterministic versus stochastic curiosity in a random world", 
                  theme = theme_pubr(base_size = 8, legend = "none"))

print(fig)

# -- Save a to pdf --=
name <- "img/determinisitic_curiosity"
ggsave(paste(name, ".pdf", sep=""), plot=fig, height = 2.6*2, width = 2*2)

rm(c1, c2)
```
# Figure - Dual value learning
- Explore/exploit as indepdendent objectives

## Load data
```{r message=FALSE, cache=TRUE}
exp_name <- "exp393"
param_codes <- 0:9
run_codes <- 1:10
file_names <- c("score_E", 
                "score_R", 
                "action", 
                "p_bests", 
                "regret", 
                "value_E", 
                "value_R", 
                "ties", 
                "policy",
                "total_E", 
                "total_R",
                "total_regret")

result393 <- load.result(exp_name, param_codes, run_codes, file_names)
result393 %>% 
  group_by(param, run) %>% 
  summarise(
    total_E=max(total_E),
    total_R=max(total_R),
    total_regret=max(total_regret),
    value_E=median(value_E),
    value_R=median(value_R),
    p_bests=max(p_bests),
    regret=median(regret[regret > 0])
  ) %>% 
  ungroup() ->
summary393
```

## Build figure
```{r, fig.height=2.25, fig.width=1.2}
result393 %>% 
  filter(run == 1, param == 1) %>% 
  # filter(global_step > 10) %>% 
  ggplot(aes(x=global_step, y=factor(policy), color=factor(policy))) +
  geom_point(size=0.8, alpha=0.5) +
  labs(x="", y="Policy") +
  scale_y_discrete(
    breaks=c(0, 1), 
    labels=c("Explore", "Exploit")) +
  lims(x=c(0, 200)) +
  scale_color_manual("", values=c("darkorchid4", "darkgrey")) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) -> p0

result393 %>% 
  filter(run == 1, param == 1) %>% 
  filter(global_step > 10) %>% 
  ggplot(aes(x=global_step, y=value_E)) +
  geom_line(size=0.8, alpha=1, color="darkorchid4") +
  lims(x=c(0, 200)) +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  labs(x="", y="Information value") + 
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) -> p1

result393 %>% 
  filter(run == 1, param == 1) %>% 
  filter(global_step > 10) %>% 
  ggplot(aes(x=global_step, y=value_R)) +
  geom_line(size=0.8, alpha=1, color="darkgrey") +
  lims(x=c(0, 200)) +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  labs(x="", y="Reward value") + 
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) -> p2

result393 %>% 
  filter(run == 1, param == 1) %>% 
  filter(global_step > 10) %>% 
  ggplot(aes(x=global_step, y=regret)) +
  geom_line(size=0.8, alpha=1, color="azure4") +
  lims(x=c(0, 200), y=c(0, 1)) +
  labs(x="Time", y="Regret") + 
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) -> p3

p0 / p1 / p2 / p3 + 
  plot_annotation(
      title="Dual value learning", 
      subtitle = "Explore/exploit with independent policies",
      theme = theme_pubr(base_size = 8, legend = "none"))

rm(p0, p1, p2, p3)
```

# Figure - Reward collection in a random world
## Load data for BanditOneHigh4 experiments
- *NOTE*: result393_4 uses BanditOneHigh10, change to BanditOneHigh4 when that data is available. 
- *NOTE*: need random data (ep=1)

### Custom loader
```{r}
load.result <- function(exp_name, param_codes, run_codes, file_names){
  num_files <- length(file_names)
  result <- NULL
  for (param in param_codes){
    for (run in run_codes) {
      runtmp <- read_csv(paste(data_path, 
                               exp_name, 
                               paste("param", param, sep=""), 
                               paste("run", run, sep=""), 
                               paste(file_names[1], "csv", sep="."), sep="/"))    
      for (name in file_names[2:num_files]){
        tmp <- read_csv(paste(data_path, 
                              exp_name, 
                              paste("param", param, sep=""), 
                              paste("run", run, sep=""), 
                              paste(name, "csv", sep="."), sep="/"))  
        runtmp[[name]] <- tmp[[name]]
      }
      runtmp$run <- run
      runtmp$param <- param
      result <- bind_rows(result, runtmp)  
    }
  }
  result
}
```

### Load
```{r, message=FALSE}
exp_name <- "exp393"
param_codes <- 0:9
run_codes <- 1:10
file_names <- c("score_E", 
                "score_R", 
                "action", 
                "p_bests", 
                "regret", 
                "value_E", 
                "value_R", 
                "ties", 
                "policy",
                "total_E", 
                "total_R",
                "total_regret")

result393 <- load.result(exp_name, param_codes, run_codes, file_names)
result393 %>% 
  group_by(param, run) %>% 
  summarise(
    total_E=max(total_E),
    total_R=max(total_R),
    total_regret=max(total_regret),
    value_E=median(value_E),
    value_R=median(value_R),
    p_bests=max(p_bests),
    regret=median(regret[regret > 0])
  ) %>% 
  ungroup() ->
summary393

# ---
exp_name <- "exp396"
param_codes <- 0:9
run_codes <- 1:10
file_names <- c("score_R", 
                "score_E", 
                "action", 
                "p_bests", 
                "regret", 
                "value_ER",
                "total_R",
                "total_E",
                "total_regret")

result396 <- load.result(exp_name, param_codes, run_codes, file_names)
result396 %>% 
  group_by(param, run) %>% 
  summarise(
    total_R=max(total_R),
    total_E=max(total_E),
    total_regret=max(total_regret),
    value_ER=median(value_ER),
    p_bests=max(p_bests),
    regret=median(regret[regret > 0])
  ) %>% 
  ungroup() ->
summary396

# ---
exp_name <- "exp397"
param_codes <- c(0)
run_codes <- 1:100
file_names <- c("score_R", 
                "action", 
                "p_bests", 
                "regret", 
                "total_R",
                "total_regret")

result397 <- load.result(exp_name, param_codes, run_codes, file_names)
result397 %>% 
  group_by(param, run) %>% 
  summarise(
    total_R=max(total_R),
    total_regret=max(total_regret),
    p_bests=max(p_bests),
    regret=median(regret[regret > 0])
  ) %>% 
  ungroup() ->
summary397

# ---
# Join all the data
result393 %>% 
  dplyr::select(
    global_step, param, run, action, total_R, 
    total_regret, p_bests) -> tmp1
result396 %>% 
  dplyr::select(
    global_step, param, run, action, total_R, 
    total_regret, p_bests) -> tmp2
result397 %>% 
  dplyr::select(
    global_step, param, run, action, total_R, 
    total_regret, p_bests) -> tmp3

tmp1$agent <- "Deterministic"
tmp2$agent <- "Stochastic"
tmp3$agent <- "Random"

result393_7 <- tmp1
result393_7 <- bind_rows(result393_7, tmp2)
rm(tmp1, tmp2, tmp3)

# ---
summary393 %>% 
  dplyr::select(param, run, total_R, total_regret, p_bests) -> tmp1
summary396 %>% 
  dplyr::select(param, run, total_R, total_regret, p_bests) -> tmp2
summary397 %>% 
  dplyr::select(param, run, total_R, total_regret, p_bests) -> tmp3

tmp1$agent <- "Deterministic"
tmp2$agent <- "Stochastic"
tmp3$agent <- "Random"

summary393_7 <- tmp1
summary393_7 <- bind_rows(summary393_7, tmp2)
summary393_7 <- bind_rows(summary393_7, tmp3)

summary393_7$agent <- factor(summary393_7$agent, 
                           levels=c("Deterministic", "Stochastic", "Random"))

rm(tmp1, tmp2, tmp3)
```

## Sub 1 - examples
```{r, fig.height=1.5, fig.width=1}
result393_7 %>% 
filter(agent == "Deterministic") %>% 
  # filter(global_step < 40) %>%
  filter(run == 1, param <= 10) %>% 
  ggplot(aes(x=global_step, y=action)) +
  geom_line(size=0.5, alpha=1, color="darkorchid4") +
  scale_x_continuous(breaks=c(0, 100, 200)) +
  labs(x="Time", y="Choice", title="Deterministic\n(Dual value)") +
  facet_wrap(.~param, ncol=1) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(0.1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(plot.title = element_text(size = 6)) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks = element_blank()) + 
  theme(legend.key.size = unit(0.2, "cm")) -> p1

result393_7 %>% 
filter(agent == "Stochastic") %>% 
  # filter(global_step < 40) %>%
  filter(run == 1, param <= 10) %>% 
  ggplot(aes(x=global_step, y=action)) +
  geom_line(size=0.5, alpha=1, color="dodgerblue4") +
  labs(x="Time", y="", title="Stochastic\n(Intrinsic reward)") +
  scale_x_continuous(breaks=c(0, 100, 200)) +
  facet_wrap(.~param, ncol=1) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(0.1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(plot.title = element_text(size = 6)) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.text.x = element_blank()) +
  # theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks = element_blank()) + 
  theme(legend.key.size = unit(0.2, "cm")) -> p2

c1 <- p1 + p2
```

## Sub 2 - dists
```{r, fig.height=1.5, fig.width=0.8}
max_R <- 200

# average value
summary393_7 %>% 
  # filter(agent %in% c("Deterministic", "Stochastic")) %>% 
  ggplot(aes(x=agent, y=total_R, color=agent)) +
  geom_jitter(size=0.3, alpha=0.9, width=0.2) +
  stat_summary(fun=median, color="black", alpha=0.9, size=2, shape="-") +
  scale_colour_manual("", 
                      values=c("mediumorchid4", "dodgerblue4", "darkgray")) +
  # lims(y=c(100, max_R)) +
  labs(x="", y="Total reward") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) +
  theme(axis.text.x = element_blank()) -> 
  p1

# average regret
summary393_7 %>% 
  # filter(agent %in% c("Deterministic", "Stochastic")) %>% 
  ggplot(aes(x=agent, y=total_regret, color=agent)) +
  geom_jitter(size=0.3, alpha=0.9, width=0.2) +
  stat_summary(fun=median, color="black", alpha=0.9, size=2, shape="-") +
  scale_colour_manual("", values=c("mediumorchid4", "dodgerblue4", "darkgray")) +
  labs(x="", y="Total regret") +
  # scale_y_log10() +
  # annotation_logticks(sides = "l") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(panel.spacing = unit(1, "lines")) ->
  p2

c2 <- p1 / p2
```

## Build figure
```{r, fig.height=1.7, fig.width=1.5}
fig <- (c1 | c2 + plot_spacer()) + 
  plot_layout(widths = c(0.75, 0.25)) +
    plot_annotation(
      title="Deterministic versus stochastic reward collection", 
                  theme = theme_pubr(base_size = 8, legend = "none"))

print(fig)

# -- Save a to pdf ---
name <- "img/reward_collection"
ggsave(paste(name, ".pdf", sep=""), plot=fig, height = 2.2*2, width = 1.5*2)

# -
# rm(c1, c2)
```