---
title: "Figures"
output: html_notebook
---

# Load library
```{r, message=FALSE}
library(zoo)
library(ggplot2)
library(ggpubr)
library(patchwork)
library(tidyr)
library(dplyr)
library(gridExtra)
library(grid)
library(readr)
library(latex2exp)
# library(MASS) 
library(scales)
library(patchwork)
options(scipen=1000000)

# Load load_result and other helpful functions
source("utils.R")

# --- Main path to all data ---
data_path <- "~/Code/infomercial/data/"
analysis_path <- "~/Code/infomercial/notebooks/"

```

# Fig. Tasks
- There are five task diagrams defined in `tasks.Rmd`. There result in ggplot objs
  that are named `task0`-`task5`. These objects are used in this notebook. To get them
  open `tasks.Rmd` and run all its cells. Only the task objects will be left in the
  shared workspace.
  

# Fig. Curiosity in a random world
# Fig. Independent policies
# Fig. Importance of boredom
# Fig. Bandits


# Old plots for easy task 1 
## Sub 1 - examples
```{r, fig.height=1.5, fig.width=1}
result393_7 %>% 
filter(agent == "Deterministic") %>% 
  # filter(global_step < 40) %>%
  filter(run == 1, param <= 10) %>% 
  ggplot(aes(x=global_step, y=action)) +
  geom_line(size=0.5, alpha=1, color="chartreuse4") +
  scale_x_continuous(breaks=c(0, 100, 200)) +
  labs(x="Time", y="Choice", title="Deterministic") +
  facet_wrap(.~param, ncol=1) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(0.1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(plot.title = element_text(size = 6)) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks = element_blank()) + 
  theme(legend.key.size = unit(0.2, "cm")) -> p1

result393_7 %>% 
filter(agent == "Stochastic") %>% 
  # filter(global_step < 40) %>%
  filter(run == 1, param <= 10) %>% 
  ggplot(aes(x=global_step, y=action)) +
  geom_line(size=0.5, alpha=1, color="chartreuse4") +
  labs(x="Time", y="", title="Stochastic") +
  scale_x_continuous(breaks=c(0, 100, 200)) +
  facet_wrap(.~param, ncol=1) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(0.1, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(plot.title = element_text(size = 6)) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.text.x = element_blank()) +
  # theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks = element_blank()) + 
  theme(legend.key.size = unit(0.2, "cm")) -> p2

c1 <- p1 + p2
```

## Sub 2 - dists
```{r, fig.height=1.5, fig.width=0.8}
num_episodes <- 200

# average value
summary393_7 %>% 
  ggplot(aes(x=agent, y=total_R/num_episodes, color=agent)) +
  geom_jitter(size=0.3, alpha=0.9, width=0.2) +
  stat_summary(fun=median, color="black", alpha=0.9, size=2, shape="-") +
  scale_colour_manual("", 
                      values=c("chartreuse4", "chartreuse4", "darkgray")) +
  lims(y=c(0,1)) +
  labs(x="", y="Total reward") +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) +
  theme(axis.text.x = element_blank()) -> 
  p1

# Total regret
summary393_7 %>% 

  ggplot(aes(x=agent, y=total_regret/num_episodes, color=agent)) +
  geom_jitter(size=0.3, alpha=0.9, width=0.2) +
  stat_summary(fun=median, color="black", alpha=0.9, size=2, shape="-") +
  scale_colour_manual("", 
                      values=c("chartreuse4", "chartreuse4", "darkgray")) +
  labs(x="", y="Total regret") +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(panel.spacing = unit(1, "lines")) ->
  p2

c2 <- p1 / p2
```

## Build figure
```{r, fig.height=1.7, fig.width=1.5}
fig <- (c1 | c2 + plot_spacer()) + 
  plot_layout(widths = c(0.75, 0.25)) +
    plot_annotation(
      title="Cusiosity and reward collection in a random world", 
      theme = theme_pubr(base_size = 8, legend = "none"))

print(fig)

# -- Save a to pdf ---
name <- "img/reward_collection"
ggsave(paste(name, ".pdf", sep=""), plot=fig, height = 2.2*2, width = 1.5*2)

# -
# rm(c1, c2)
```


# Figure 4 - Reward collection in difficult envinronments
- Harder problems, using a broader range of exploration strategies
- Only show final results
- Need cartoons

## Load data
### Load
```{r, message=FALSE}
# --- Init files ---

# The exps are:
exp_names <- c("exp393", 
               "exp394", 
               "exp395", 
               "exp396", 
               "exp397")
agent_names <- c("Curiosity", 
                 "del-Random", 
                 "tau-Random", 
                 "Intrinsic", 
                 "Random")

# These are shared in all models, but Random.
param_codes <- 0:9
run_codes <- 1:10

# Load only data every model has:
file_names <- c("action", 
                "p_bests", 
                "regret", 
                "total_R",
                "total_regret")

# -- Load ---
bandit_results <- NULL

# 1. Load random first (diff file structure)
bandit_results <- load.result(exp_names[5], c(0), 1:100, file_names)
bandit_results$exp <- exp_names[5]
bandit_results$agent <- agent_names[5]

# 2. then load the rest
for(i in 1:length(exp_names[1:4])){
  result <- load.result(exp_names[i], param_codes, run_codes, file_names)
  result$exp <- exp_names[i]
  result$agent <- agent_names[i]
  bandit_results <- bind_rows(bandit_results, result)
  rm(result)
}

# 3. summarize 
bandit_results %>% 
  group_by(agent, param, run) %>% 
  summarise(
    total_R=last(total_R),
    total_regret=last(total_regret),
    p_bests=last(p_bests)
  ) %>% 
  ungroup() ->
bandit_summary

# Reorder names
ordered_names <- c("Curiosity",
                   "Intrinsic", 
                   "tau-Random", 
                   "del-Random", 
                   "Random")
ordered_colors <- c("chartreuse4", 
                    "chartreuse4", 
                    "goldenrod4", 
                    "darkgoldenrod3", 
                    "darkgrey")
bandit_results$agent <- factor(bandit_results$agent, levels = ordered_names)
bandit_summary$agent <- factor(bandit_summary$agent, levels = ordered_names)

# 5. Cleanup
rm(file_names, agent_names, exp_names, param_codes, run_codes, i)
```

### Sub 1 - actions examples
```{r, fig.width=1.8, fig.height=1.6}
bandit_results %>% 
  filter(agent != "Random") %>% 
  filter(run <= 10, param == 0) %>% 
  ggplot(aes(x=global_step, y=action, color=agent)) +
  geom_line(size=0.6, alpha=1) +
  labs(x="Time", y="Choice") +
  facet_grid(run~agent) +
  scale_colour_manual("", values=ordered_colors) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(panel.spacing = unit(0.24, "lines")) +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  theme(legend.box.background = element_rect(colour = "black", size=1)) +
  theme(plot.title = element_text(size = 6)) +
  theme(strip.text.y = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks = element_blank()) + 
  theme(legend.key.size = unit(0.2, "cm")) -> sub1
```

### Sub 2 - value summary
```{r, fig.width=1.2, fig.height=1.6}
num_episodes <- 200

## Values
bandit_summary %>% 
  ggplot(aes(x=agent, y=total_R/num_episodes, color=agent)) +
  geom_jitter(size=0.01, alpha=0.5, width=0.3) +
  stat_summary(fun=median, alpha=1, color="black", size=2, shape="-") +
  scale_colour_manual("", values=ordered_colors) +
  labs(y="Total reward", x="") +
  lims(y=c(0, 1)) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(panel.spacing = unit(1, "lines")) -> p1

bandit_summary %>% 
  ggplot(aes(x=agent, y=total_regret/num_episodes, color=agent)) +
  geom_jitter(size=0.01, alpha=0.5, width=0.3) +
  stat_summary(fun=median, alpha=1, color="black", size=2, shape="-") +
  scale_colour_manual("", values=ordered_colors) +
  labs(y="Total regret", x="") +
  lims(y=c(0, 1)) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(panel.spacing = unit(1, "lines")) -> p2

bandit_summary %>% 
  ggplot(aes(x=agent, y=p_bests, color=agent)) +
  geom_jitter(size=0.05, alpha=0.5, width=0.3) +
  stat_summary(fun=median, alpha=1, color="black", size=2, shape="-") +
  scale_colour_manual("", values=ordered_colors) +
  labs(y="Best choice", x="") +
  lims(y=c(0, 1)) +
  theme_pubr(base_size = 6, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") + 
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(panel.spacing = unit(1, "lines")) -> p3

sub2 <- p1 / p2 
```

### Build
```{r, fig.width=2.6, fig.height=2.4}
sub1 + (sub2 + plot_spacer()) + 
  plot_layout(widths = c(0.8, 0.2)) + 
  plot_annotation(
      title="Task 1 - reward collection with a high payout", 
                  theme = theme_pubr(base_size = 8, legend = "none"))
```


# Figure 5 - Hard envionments, under unexpected time pressure.
- Reuse HPs from Figure 4.
- Is curiosity a problem here?
- TODO
## Load data
```{r}

```


# Supp 1 - Sto v Det in reward collection
# Supp 2 - Forcing determinism stocastic actors
- Can this help?
