---
title: "Figures"
output: html_notebook
---

# Libraries
```{r, message=FALSE}
library(ggplot2)
library(patchwork)
library(tidyr)
library(dplyr)
library(patchwork)
library(ggthemes)
library(ggpubr)
library(gridExtra)
library(grid)
library(readr)
library(latex2exp)
library(MASS) 
library(scales)

options(scipen=1000000)

kl_divergence <- function(p, q) {
  sum(p * log(p/q))
}
```


# Load data
```{r, eval=TRUE, echo=FALSE, message=FALSE}
data_path <- "~/Code/infomercial/data/"

# ----------------------------------------------------------------------------
# Load example traces
# All values for eta only
value_traces <- read_csv(paste(data_path, "example_value_traces_eta_BanditOneHigh10-v0.csv", sep=""))
value_traces$env <- rep("BanditOneHigh10-v0", nrow(value_traces))

# Get indiv. files
example_trace1 <- read_csv(paste(data_path, "example_traces_epsilon_BanditOneHigh10-v0.csv", sep=""))
example_trace1$env <- rep("BanditOneHigh10-v0", nrow(example_trace1))
example_trace2 <-read_csv(paste(data_path, "example_traces_eta_BanditOneHigh10-v0.csv", sep=""))
example_trace2$env <- rep("BanditOneHigh10-v0", nrow(example_trace2))
example_trace3 <- read_csv(paste(data_path, "example_traces_softbeta_BanditOneHigh10-v0.csv", sep=""))  
example_trace3$env <- rep("BanditOneHigh10-v0", nrow(example_trace3))

example_trace4 <- read_csv(paste(data_path, "example_traces_epsilon_BanditTwoHigh10-v0.csv", sep=""))
example_trace4$env <- rep("BanditTwoHigh10-v0", nrow(example_trace4))
example_trace5 <- read_csv(paste(data_path, "example_traces_eta_BanditTwoHigh10-v0.csv", sep=""))
example_trace5$env <- rep("BanditTwoHigh10-v0", nrow(example_trace5))
example_trace6 <- read_csv(paste(data_path, "example_traces_softbeta_BanditTwoHigh10-v0.csv", sep=""))
example_trace6$env <- rep("BanditTwoHigh10-v0", nrow(example_trace6))

example_trace7 <- read_csv(paste(data_path, "example_traces_epsilon_BanditHardAndSparse10-v0.csv", sep=""))
example_trace7$env <- rep("BanditHardAndSparse10-v0", nrow(example_trace7))
example_trace8 <- read_csv(paste(data_path, "example_traces_eta_BanditHardAndSparse10-v0.csv", sep=""))
example_trace8$env <- rep("BanditHardAndSparse10-v0", nrow(example_trace8))
example_trace9 <- read_csv(paste(data_path, "example_traces_softbeta_BanditHardAndSparse10-v0.csv", sep=""))
example_trace9$env <- rep("BanditHardAndSparse10-v0", nrow(example_trace9))

example_trace10 <- read_csv(paste(data_path, "example_traces_epsilon_BanditUniform121-v0.csv", sep=""))
example_trace10$env <- rep("BanditUniform121-v0", nrow(example_trace10))
example_trace11 <- read_csv(paste(data_path, "example_traces_eta_BanditUniform121-v0.csv", sep=""))
example_trace11$env <- rep("BanditUniform121-v0", nrow(example_trace11))
example_trace12 <- read_csv(paste(data_path, "example_traces_softbeta_BanditUniform121-v0.csv", sep=""))
example_trace12$env <- rep("BanditUniform121-v0", nrow(example_trace12))
  
# Join 'em
example_traces <- rbind(
  example_trace1,
  example_trace2,
  example_trace3,
  example_trace4,
  example_trace5,
  example_trace6,
  example_trace7,
  example_trace8,
  example_trace9,
  example_trace10,
  example_trace11,
  example_trace12
)
example_traces$agents <- factor(example_traces$agents, levels=c("eta", "softbeta", "epsilon"))

# Free memory
rm(
  example_trace1,
  example_trace2,
  example_trace3,
  example_trace4,
  example_trace5,
  example_trace6,
  example_trace7,
  example_trace8,
  example_trace9,
  example_trace10,
  example_trace11,
  example_trace12
)
```

```{r, message=FALSE}
bandit_names <- c("BanditOneHigh10-v0", "DeceptiveBanditOneHigh10-v0", "BanditUniform121-v0",
                  "BanditHardAndSparse10-v0")

traces <- NULL
total <- NULL
critic <- NULL
bandit <- NULL
for(bandit_name in bandit_names){
  tmp <- read_csv(paste(data_path, "table_total_", bandit_name, ".csv", sep=""))
  tmp$env <- rep(bandit_name, nrow(tmp))
  total <- rbind(total, tmp)
  
  tmp <- read_csv(paste(data_path, "table_critic_", bandit_name, ".csv", sep=""))
  tmp$env <- rep(bandit_name, nrow(tmp))
  critic <- rbind(critic, tmp)
  
  tmp <- read_csv(paste(data_path, "table_bandit_", bandit_name, ".csv", sep=""))
  tmp$env <- rep(bandit_name, nrow(tmp))
  bandit <- rbind(bandit, tmp)
}

# Set agent order
total$agents <- factor(total$agents, 
                       levels=rev(c("eta", "softbeta", "epsilon", "anneal-epsilon", "random")))
critic$agents <- factor(critic$agents, 
                        levels=rev(c("eta", "softbeta", "epsilon", "anneal-epsilon", "random")))

paper_names <- c("dual value", "bayesian", "e-greedy", "anneal-e", "random")
total$agents <- recode(total$agents, 
                       eta=paper_names[1], 
                       softbeta=paper_names[2], 
                       epsilon=paper_names[3], 
                       'anneal-epsilon'=paper_names[4], 
                       random=paper_names[5])

rm(tmp)
```

# Fig - Bee cartoon
This is dummy section; see image itself.

# Fig - Deterministic versus random exploration
....When the goal is only learning.
## Load
```{r, message=FALSE}
data_path <- "~/Code/infomercial/data/"
# num_episodes <- 140

file_names <- c("score_E", "action", "p_bests", "regret", "value_E", "ties")

exp_name <- "exp326"
result326 <- read_csv(paste(data_path, exp_name, paste(file_names[1], "csv", sep="."), sep="/"))
for(name in file_names[2:6]){
  tmp <- read_csv(paste(data_path, exp_name, paste(name, "csv", sep="."), sep="/"))
  result326[[name]] <- tmp[[name]]
}
result326$exp <- "Deterministic"

exp_name <- "exp327"
result327 <- read_csv(paste(data_path, exp_name, paste(file_names[1], "csv", sep="."), sep="/"))
for(name in file_names[2:6]){
  tmp <- read_csv(paste(data_path, exp_name, paste(name, "csv", sep="."), sep="/"))
  result327[[name]] <- tmp[[name]]
}
result327$exp <- "Stocastic"

# Truncate to Det samples
result327 <- filter(result327, global_step < nrow(result326))
```

## Plot
```{r, fig.width=2.4, fig.height=2.1}
# ---
result327 %>% 
  ggplot(aes(x=global_step, y=action+1)) +
  geom_point(size=0.6, color="dodgerblue4") +
  # geom_line(size=0.2, color="dodgerblue4") +
  labs(x="Trial", y="Arm", tag="a.") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(plot.tag = element_text(size=10, face="bold")) +
  theme(plot.title = element_text(vjust=3, hjust = 0.0, size=8)) +
  theme(panel.spacing = unit(0.75, "lines")) +
  theme(strip.background = element_blank()) +
  theme(strip.text.x = element_blank()) +
  theme(strip.text.y = element_text(angle = 0)) -> p1

result326 %>% 
  ggplot(aes(x=global_step, y=action+1)) +
  geom_point(size=0.6, color="darkorchid4") + 
  # geom_line(size=0.2, color="darkorchid4") +
  labs(x="Trial", y="Arm", tag="b.") +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(plot.tag = element_text(size=10, face="bold")) +
  theme(plot.title = element_text(vjust=3, hjust = 0.0, size=8)) +
  theme(panel.spacing = unit(0.75, "lines")) +
  theme(strip.background = element_blank()) +
  theme(strip.text.x = element_blank()) +
  theme(strip.text.y = element_text(angle = 0)) -> p2

# --
full_join(result326, result327) -> tmp
tmp %>% 
  ggplot(aes(x=global_step, y=log10(value_E), color=exp)) +
  geom_point(size=0.6, alpha=.9, alpha=.9) +
  geom_line(size=0.2) +
  labs(x="Trial", y="Info value", tag="c.") + 
  scale_color_manual("Mode", values=c("darkorchid4", "dodgerblue4")) +
  theme_pubr(base_size = 8, legend = "right") +
  theme(strip.background = element_blank()) +
  theme(plot.tag = element_text(size=10, face="bold")) -> p3
# print(p1)

full_join(result326, result327) -> tmp
tmp %>% 
  ggplot(aes(x=global_step, y=regret, color=exp)) +
  geom_point(size=0.6, alpha=.9, alpha=.9) +
  geom_line(size=0.2) +
  labs(x="Trial", y="Regret", tag="d.") + 
  scale_color_manual("Mode", values=c("darkorchid4", "dodgerblue4")) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(plot.tag = element_text(size=10, face="bold")) -> p4

# ---
full_join(result326, result327) %>% 
  group_by(exp) %>% 
  summarise(total_E = sum(score_E),
            total_regret = sum(regret)) %>% 
  ungroup() ->
  tmp

tmp %>% 
  ggplot(aes(x=exp, y=total_E, fill=exp)) +
  geom_bar(stat = "identity", width=0.8) +
  scale_fill_manual("",  values=c("darkorchid4", "dodgerblue4")) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  labs(x="", y="Total value", tag="e.") +
  theme(strip.background = element_blank()) +
  coord_flip() ->
  p5

tmp %>% 
  ggplot(aes(x=exp, y=total_regret, fill=exp)) +
  geom_bar(stat = "identity", width=0.8) +
  scale_fill_manual("",  values=c("darkorchid4", "dodgerblue4")) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  labs(x="", y="Total regret", tag="f.") +
  coord_flip() ->
  p6

p5 + p6
(p1 + p2) / p3 / p4 + plot_annotation(title="Deterministic versus stocastic curiosity", theme = theme_pubr(base_size = 8))
```

# Fig - Curiosity in a random world
## Load
```{r, message=FALSE}
file_names <- c("score_E", "action", "p_bests", "regret", "value_E", "ties")
run_names <- c("run1", "run2", "run3", "run4", "run5", "run6")

exp_name <- "exp328"
result328 <- NULL
for (run in run_names){
  runtmp <- read_csv(paste(data_path, exp_name, run, paste(file_names[1], "csv", sep="."), sep="/"))
  for (name in file_names[2:6]){
    tmp <- read_csv(paste(data_path, exp_name, run, paste(name, "csv", sep="."), sep="/"))  
    runtmp[[name]] <- tmp[[name]]
  }
  runtmp$run <- run
  result328 <- bind_rows(result328, runtmp)  
}
rm(runtmp, tmp)
```
## Plot
```{r, fig.height=1.5, fig.width=1.8}
result328 %>% 
  filter(global_step < 40) %>% 
  ggplot(aes(x=global_step, y=action+1)) +
  geom_point(size=0.3, color="black") + 
  labs(x="Trials", y="Arm", title="Deterministic curiosity\nin a random world") +
  scale_y_continuous(breaks=c(1, 4), labels=c(1,4)) +
  facet_wrap(.~run, ncol=1) +
  theme_pubr(base_size = 8, legend = "none") +
  theme(strip.background = element_blank()) +
  theme(plot.tag = element_text(size=10, face="bold")) +
  theme(plot.title = element_text(vjust=3, hjust = 0.0, size=8)) +
  theme(panel.spacing = unit(0.75, "lines")) +
  theme(strip.background = element_blank()) +
  theme(strip.text.x = element_blank()) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme() -> p1
# plot(p1)

result328 %>% 
  filter(global_step < 40) %>% 
  ggplot(aes(x=action+1)) +
  geom_bar(width=0.9) + 
  labs(x="Arm", y="Relative count", title="40 episodes") +
  theme_pubr(base_size=8, legend = "none")  +
  theme(text = element_text(color = "black")) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.background = element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks.y = element_blank()) +
  theme(plot.title = element_text(vjust = -3, hjust = 0, size = 6)) +
  facet_grid(run~.) -> p2
# print(p2)

result328 %>% 
  ggplot(aes(x=action+1)) +
  geom_bar(width=0.9) + 
  labs(x="Arm", y="", title="4000 episodes") +
  theme_pubr(base_size=8, legend = "none")  +
  theme(text = element_text(color = "black")) +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.background = element_blank()) +
  # theme(strip.text.y = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks.y = element_blank()) +
  theme(plot.title = element_text(vjust = -3, hjust = 0.5, size = 6)) +
  facet_grid(run~.) -> p3
# print(p3)

(p1 | (p2 + p3)) + 
  plot_layout(widths = c(0.5, 0.5)) 
```
# Fig - Generic 10 cartoon
Create and plot a generic 10 armed bandit used only to explain the task.
```{r, fig.height=0.8, fig.width=0.7, fig.}
fig <- NULL
generic <- data.frame(arms=0:9, p_reward=runif(10, min=0.1, max=0.6))
generic$p_reward[8] <- 0.8

generic %>% 
  ggplot(aes(x=as.factor(arms+1), y=p_reward)) +
  geom_bar(stat="identity", width=0.6, fill="black") +
  geom_point(aes(x=8, y=0.9), color="red", size=0.5, alpha=0.9) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_x_discrete(breaks=c(1, 10), labels=c(1, 10)) +
  labs(x="Arm", y="Average\nReward") +
  coord_flip() -> bandit1

fig <- bandit1 +
  plot_annotation(title = "Payout",
                  theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)
```

# Fig - Simple 10 cartoon
```{r, fig.height=0.8, fig.width=0.7, fig.}
fig <- NULL

bandit %>% 
  filter(env == "BanditOneHigh10-v0") %>% 
  ggplot(aes(x=as.factor(arms+1), y=p_reward)) +
  geom_bar(stat="identity", width=0.6, fill="black") +
  geom_point(aes(x=8, y=0.9), color="red", size=0.5, alpha=0.9) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_x_discrete(breaks=c(1, 10), labels=c(1, 10)) +
  labs(x="Arm", y="Average\nReward") +
  coord_flip() -> bandit1

fig <- bandit1 +
  plot_annotation(title = "Simple 10",
                  theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "simple10-bandit"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*0.8, width = 2*0.7)

# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*0.8, width = 2*0.7, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*0.8, width = 2*0.7, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Simple 10 value example
```{r, fig.height=0.8, fig.width=1.2}
fig <- NULL
value_traces %>% 
  filter(n==3) %>% 
  filter(episodes < 100) %>% 
  ggplot(aes(x=episodes, y=log10(values_R))) +
  geom_point(size=0.5, color="black", alpha=.9) +
  geom_point(aes(x=episodes, y=log10(values_E)), size=0.5, color="darkorchid4", alpha=.9) +
  labs(x="Trial", y="log Value") + 
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold")) -> value1

fig <- value1 +
  plot_annotation(title = "Dual value in action",
                  theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "simple10-value_example"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*0.8, width = 2*1.2)

# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*0.8, width = 2*1.2, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*0.8, width = 2*1.2, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Simple 10 exploration examples
## n=10
```{r, fig.height=3.2, fig.width=2.6}
fig <- NULL
value_traces %>% 
  filter(n < 10) %>%
  filter(episodes < 50) %>% 
  ggplot(aes(x=episodes, y=arms+1)) +
  geom_point(size=0.3, color="black") + 
  labs(x="Trial", y="Arm choice", title="dual value") +
  scale_y_continuous(breaks=c(1, 10), labels=c(1,10)) +
  facet_wrap(.~n, ncol=1) +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.spacing = unit(.35, "lines"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  geom_hline(aes(yintercept=8), color="red", size=.1, alpha=0.95) +
  theme() -> p1

example_traces %>% 
  filter(env == "BanditOneHigh10-v0", agents=="epsilon") %>% 
  filter(n < 10) %>%
  filter(episodes < 50) %>% 
  ggplot(aes(x=episodes, y=arms+1)) +
  geom_point(size=0.3, color="black") + 
  labs(x="Trial", y="Arm choice", title="e-greedy") +
  scale_y_continuous(breaks=c(1, 10), labels=c(1,10)) +
  facet_wrap(.~n, ncol=1) +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.spacing = unit(.35, "lines"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  geom_hline(aes(yintercept=8), color="red", size=.1, alpha=0.95) +
  theme() -> p2

example_traces %>% 
  filter(env == "BanditOneHigh10-v0", agents=="softbeta") %>% 
  filter(n < 10) %>%
  filter(episodes < 50) %>% 
  ggplot(aes(x=episodes, y=arms+1)) +
  geom_point(size=0.3, color="black") + 
  labs(x="Trial", y="Arm choice", title="bayesian") +
  scale_y_continuous(breaks=c(1, 10), labels=c(1,10)) +
  facet_wrap(.~n, ncol=1) +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.spacing = unit(.35, "lines"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  geom_hline(aes(yintercept=8), color="red", size=.1, alpha=0.95) +
  theme() -> p3

fig <- p1 + p2 + p3 +
  plot_annotation(tag_levels = 'a', tag_suffix = ".") + 
  plot_annotation(title = "Exploration in action",
                  theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "simple10-exploration_example_n10"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*3.2, width = 2*2.6)

# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*3.2, width = 2*2.6, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*3.2, width = 2*2.6, standAlone = FALSE)
plot(fig)
dev.off()
```

## n=6
```{r, fig.height=2, fig.width=2.6}
fig <- NULL
value_traces %>% 
  filter(n < 6) %>%
  filter(episodes < 50) %>% 
  ggplot(aes(x=episodes, y=arms+1)) +
  geom_point(size=0.3, color="black") + 
  labs(x="Trial", y="Arm choice", title="dual value") +
  scale_y_continuous(breaks=c(1, 10), labels=c(1,10)) +
  facet_wrap(.~n, ncol=1) +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.spacing = unit(.35, "lines"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  geom_hline(aes(yintercept=8), color="red", size=.1, alpha=0.95) +
  theme() -> p1

example_traces %>% 
  filter(env == "BanditOneHigh10-v0", agents=="epsilon") %>% 
  filter(n < 6) %>%
  filter(episodes < 50) %>% 
  ggplot(aes(x=episodes, y=arms+1)) +
  geom_point(size=0.3, color="black") + 
  labs(x="Trial", y="Arm choice", title="e-greedy") +
  scale_y_continuous(breaks=c(1, 10), labels=c(1,10)) +
  facet_wrap(.~n, ncol=1) +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.spacing = unit(.35, "lines"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  geom_hline(aes(yintercept=8), color="red", size=.1, alpha=0.95) +
  theme() -> p2

example_traces %>% 
  filter(env == "BanditOneHigh10-v0", agents=="softbeta") %>% 
  filter(n < 6) %>%
  filter(episodes < 50) %>% 
  ggplot(aes(x=episodes, y=arms+1)) +
  geom_point(size=0.3, color="black") + 
  labs(x="Trial", y="Arm choice", title="bayesian") +
  scale_y_continuous(breaks=c(1, 10), labels=c(1,10)) +
  facet_wrap(.~n, ncol=1) +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.spacing = unit(.35, "lines"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  geom_hline(aes(yintercept=8), color="red", size=.1, alpha=0.95) +
  theme() -> p3

fig <- p1 + p2 + p3 +
  plot_annotation(tag_levels = 'a', tag_suffix = ".") + 
  plot_annotation(title = "Exploration in action",
                  theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "simple10-exploration_example_n6"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*2, width = 2*2.6)

# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*2, width = 2*2.6, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*2, width = 2*2.6, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Simple 10 results
```{r, fig.height=1.4, fig.width=1.2}
fig <- NULL

total %>% 
  filter(env == "BanditOneHigh10-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(total_R), SD=mad(total_R)) %>% 
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
        # axis.text.y=element_blank(),
        plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .4, .1, .1, "cm")) +
  labs(x="Model", y="Total reward") +
  geom_hline(aes(yintercept=max(M)), color="black", size=.2) +
  scale_color_manual(
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> reward1

# Build Regret panels
total %>% 
  # Stats
  filter(env == "BanditOneHigh10-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(regrets), SD=mad(regrets)) %>% 
  # Plots
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
         plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .1, .1, .1, "cm")) +
  labs(x="Model", y="Total regret") +
  scale_y_continuous(breaks=c(0, 100, 200), limits = c(0, 250)) +
  geom_hline(aes(yintercept=0), color="black", size=.2) +
  scale_color_manual(
    "Agent",
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> regret1

fig <- (reward1 / regret1) +
  plot_annotation(tag_levels = 'a', 
                  tag_suffix = ".", 
                  title = "Simple 10 results",
                  theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "simple10-results"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*1.4, width = 2*1.2)

# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*1.4, width = 2*1.2, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*1.4, width = 2*1.2, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Random 121 cartoon
```{r, fig.height=2.6, fig.width=0.75}
fig <- NULL

bandit %>% 
  filter(env == "BanditUniform121-v0") %>% 
  ggplot(aes(x=as.factor(arms+1), y=p_reward)) +
  geom_point(aes(x=55, y=0.9), color="red", size=0.5, alpha=0.9) +
  geom_bar(stat="identity", width=0.6, fill="black") +
  theme_classic() +
  scale_y_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_x_discrete(breaks=c(1, 121), labels=c(1, 121)) +
  labs(x="Arm", y="Average\nreward") +
  coord_flip() -> bandit2

fig <- bandit2 + plot_annotation(title="Random 121", 
                                 theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "random121-bandit"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*2.2, width = 2*0.75)
# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*2.2, width = 2*0.75, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*2.2, width = 2*0.75, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Random 121 results
```{r, fig.height=1.4, fig.width=1.2}
fig <- NULL

total %>% 
  filter(env == "BanditUniform121-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(total_R), SD=mad(total_R)) %>% 
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
        # axis.text.y=element_blank(),
        plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .4, .1, .1, "cm")) +
  labs(x="Model", y="Total reward") +
  scale_y_continuous(breaks=c(0, 50000/2, 50000), limits = c(0, 50000)) +
  geom_hline(aes(yintercept=max(M)), color="black", size=.2) +
  scale_color_manual(
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> reward2

# Build Regret panels
total %>% 
  # Stats
  filter(env == "BanditUniform121-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(regrets), SD=mad(regrets)) %>% 
  # Plots
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
        plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .1, .1, .1, "cm")) +
  labs(x="Model", y="Total regret") +
  scale_y_continuous(breaks=c(0, 6000/2, 6000), limits = c(0, 7000)) +
  geom_hline(aes(yintercept=0), color="black", size=.2) +
  scale_color_manual(
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> regret2

fig <- (reward2 / regret2) +
  plot_annotation(tag_levels = 'a', 
                  tag_suffix = ".", 
                  title = "Random 121 results", theme=theme(plot.title = element_text(hjust = 0.5))) 
plot(fig)

# -----------------------------------------------------------------------------------
name <- "random121-results"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*1.4, width = 2*1.2)

# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*1.4, width = 2*1.2, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*1.4, width = 2*1.2, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Sparse 10 cartoon
```{r, fig.height=0.8, fig.width=0.7}
fig <- NULL

bandit %>% 
  filter(env == "BanditHardAndSparse10-v0") %>% 
  ggplot(aes(x=as.factor(arms+1), y=p_reward)) +
  geom_bar(stat="identity", width=0.6, fill="black") +
  geom_point(aes(x=8, y=0.05), color="red", size=0.5, alpha=0.9) +
  theme_classic() +
  scale_y_continuous(breaks=c(0, 0.05, 1), limits = c(0, .05)) +
  scale_x_discrete(breaks=c(1, 10), labels=c(1, 10)) +
  labs(x="Arm", y="Average\nreward") +
  coord_flip() -> bandit3
fig <- bandit3 + plot_annotation(title="Sparse 10",
                                 theme=theme(plot.title = element_text(hjust = 0.5)))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "sparse10-bandit"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*0.8, width = 2*0.7)
# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*0.8, width = 2*0.7, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*0.8, width = 2*0.7, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Sparse 10 results
```{r, fig.height=1.6, fig.width=1.2}
fig <- NULL

total %>% 
  # Stats
  filter(env == "BanditHardAndSparse10-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(total_R), SD=mad(total_R)) %>% 
  # Plots
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
        plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .1, .1, .1, "cm")) +
  labs(x="Model", y="Total reward") +
  # scale_y_continuous(breaks=c(0, 1000/2, 1000), limits = c(0, 1000)) +
  geom_hline(aes(yintercept=max(M)), color="black", size=.2) +
  scale_color_manual(
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> reward3

total %>% 
  # Stats
  filter(env == "BanditHardAndSparse10-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(regrets), SD=mad(regrets)) %>% 
  # Plots
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
        plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .1, .1, .1, "cm")) +
  labs(x="Model", y="Total regret") +
  # scale_y_continuous(breaks=c(0, 3000/2, 3000), limits = c(0, 5000)) +
  geom_hline(aes(yintercept=0), color="black", size=.2) +
  scale_color_manual(
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> regret3

fig <- (reward3 / regret3) +
  plot_annotation(tag_levels = 'a', 
                  tag_suffix = ".", 
                  title = "Sparse 10 results",
                  theme=theme(plot.title = element_text(hjust = 0.5))
                  ) 
plot(fig)

# -----------------------------------------------------------------------------------
name <- "sparse10-results"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*1.6, width = 2*1.2)
# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*1.6, width = 2*1.2, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*1.6, width = 2*1.2, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig - Deception 10 cartoon
```{r, fig.height=1.8, fig.width=2.1}
fig <- NULL

deception_value <- data.frame(
  max_value=c(
    rev(seq(0,1,.1)), 
    seq(0,0.9,.1), 
    rep(1,10), 
    rep(1,31)),
  arm=c(
    rep("Arm 8",31), 
    c(rep("Rest",31))), 
  episodes=c(1:31, 1:31))

deception_expected_value <- data.frame(
  arms=1:10,
  expected_value=rep(0.2,10))
deception_expected_value$expected_value[8] = 0.4

# This bandit Has the same prob structure as Simple10
bandit %>% 
  filter(env == "BanditOneHigh10-v0") %>% 
  ggplot(aes(x=as.factor(arms+1), y=p_reward)) +
  geom_bar(stat="identity", width=0.6, fill="black") +
  theme_classic() +
  scale_y_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_x_discrete(breaks=c(1, 10), labels=c(1, 10)) +
  labs(x="Arm", y="Reward\nprobability") +
  coord_flip() -> bandit4

# But has as changing value structure
deception_value %>% 
  ggplot(aes(x=episodes, y=max_value)) +
  geom_line(size=.8) +
  facet_grid(arm~.) +
  theme_classic() +
  theme(strip.text.y = element_text(angle = 0)) +
  theme(strip.background = element_blank()) +
  scale_y_continuous(breaks=c(0, 0.5, 1), limits = c(-.1, 1.1)) +
  labs(x="Trial", y="Max reward\nvalue") -> value4

deception_expected_value %>% 
  ggplot(aes(x=as.factor(arms), y=expected_value)) +
  geom_bar(stat="identity", width=0.6, fill="black") +
  geom_point(aes(x=8, y=0.9), color="red", size=0.5, alpha=0.9) +
  theme_classic() +
  scale_y_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_x_discrete(breaks=c(1, 10), labels=c(1, 10)) +
  labs(x="Arm", y="Average\nreward") +
  coord_flip() -> expected4

fig <- ((bandit4 / expected4) | (value4)) + 
  plot_annotation(tag_levels = 'a', 
                  tag_suffix = ".",
                  plot_annotation(title = "Deception 10",
                  theme=theme(plot.title = element_text(hjust = 0.5)))) +
  plot_layout(heights = c(1,3))
plot(fig)

# -----------------------------------------------------------------------------------
name <- "deception-10-bandit"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*1.8, width = 2*2.1)
# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*1.8, width = 2*2.1, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*1.8, width = 2*2.1, standAlone = FALSE)
plot(fig)
dev.off()
```

# Fig Deception 10 results
```{r, fig.height=1.6, fig.width=1.2}
fig <- NULL

total %>% 
  # Stats
  filter(env == "DeceptiveBanditOneHigh10-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(total_R), SD=mad(total_R)) %>% 
  # Plots
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
        plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .1, .1, .1, "cm")) +
  labs(x="Model", y="Total reward") +
  scale_y_continuous(breaks=c(0, 50/2, 50), limits = c(0, 50)) +
  geom_hline(aes(yintercept=max(M)), color="black", size=.2) +
  scale_color_manual(
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> reward3

total %>% 
  # Stats
  filter(env == "DeceptiveBanditOneHigh10-v0") %>% 
  group_by(agents, env) %>% 
  summarise(M = median(regrets), SD=mad(regrets)) %>% 
  # Plots
  ggplot(aes(x=agents, y=M, color=agents)) +
  geom_point(alpha=1, size=1.5) +
  geom_linerange(aes(ymin=M-SD, ymax=M+SD)) +
  theme_classic() +
  theme(legend.position="none",
        plot.tag = element_text(size=14, face="bold"),
        plot.margin = margin(.1, .1, .1, .1, "cm")) +
  labs(x="Model", y="Total regret") +
  scale_y_continuous(breaks=c(0, 50/2, 50), limits = c(0, 50)) +
  geom_hline(aes(yintercept=0), color="black", size=.2) +
  scale_color_manual(
    values=rev(c("darkorchid4", "mediumpurple3", "mediumpurple1", "steelblue3", "steelblue1", "grey"))) +
  coord_flip() -> regret3

fig <- (reward3 / regret3) +
  plot_annotation(tag_levels = 'a', 
                  tag_suffix = ".", 
                  title = "Deception 10 results",
                  theme=theme(plot.title = element_text(hjust = 0.5))
                  ) 
plot(fig)

# -----------------------------------------------------------------------------------
name <- "deception010-results"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*1.6, width = 2*1.2)
# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*1.6, width = 2*1.2, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*1.6, width = 2*1.2, standAlone = FALSE)
plot(fig)
dev.off()
```
# Supplementary 
## Subfig1 - World model and distance
```{r, fig.height=1, fig.width=2.2, message=FALSE}
fig <- NULL

# Set seed for consisten Fig.
set.seed(3124)

# ------------------------------------------------------------
# World model
# Build an empty memory
ps <- runif(10)
ps <- ps / sum(ps)

ps[7] <- ps[7]+.5
ps <- ps / sum(ps)
example_memory <- data.frame(arms=1:10, p_reward=ps)

example_memory %>% 
  ggplot(aes(x=as.factor(arms), y=p_reward)) +
  geom_bar(stat="identity", width=0.6, position = "dodge", fill="black") +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold"),
        plot.title = element_text(hjust = 0.5)) +
  labs(x="Arm", y="Reward\nprobability", title="World model", tag="a.") +
  scale_y_continuous(breaks=c(0, 0.25, 0.5), limits = c(0, 0.5)) -> memory1

# ------------------------------------------------------------
# Distance
# Build an empty memory
ps <- runif(10)
ps <- ps / sum(ps)
distance_memory <- data.frame(arms=1:10, p_reward=ps)
distance_memory$memory <- rep("M_0", nrow(distance_memory))

del_p <- 0.1
n_samples <- 10000
Es <- NULL
dPs <- NULL
for(t in 1:n_samples){
  qs <- ps
  qs[7] <- qs[7] + del_p
  qs <- qs / sum(qs)  
  
  E <- kl_divergence(qs, ps)
  
  Es <- c(Es, E)
  dPs <- c(dPs, sum(abs(qs - ps)))
  
  ps <- qs
}

flux <- data.frame(E=Es, dP=dPs)

xmax <- max(flux$dP)

flux %>% 
  ggplot(aes(dP, E)) +
  geom_line(size=1.25, color="darkorchid4") +
  theme_classic() +
  theme(plot.tag = element_text(size=14, face="bold"), 
        plot.title = element_text(hjust = 0.5)) +
  labs(x="Change probability", y="KL", title="Distance", tag="b.") -> distance1

fig <- memory1 + distance1 +
  plot_annotation(tag_levels = 'a', tag_suffix = ".") 
plot(fig)

# -----------------------------------------------------------------------------------
name <- "world_model"

# Save a png
ggsave(paste(name, ".png", sep=""), plot=fig, height = 2*1.0, width = 2*2.2)
# Save a tex
tikz(file = paste(name, "_standalone.tex", sep=""), height = 2*1.0, width = 2*2.2, standAlone = TRUE)
plot(fig)
dev.off()
tikz(file = paste(name, ".tex", sep=""), height = 2*1.0, width = 2*2.2, standAlone = FALSE)
plot(fig)
dev.off()
```
